Interactive Data Exploration with Smart Drill-Down (Extended Version)

### 2016-07-25 TableSummarization/journalVersion/smartDrillDown.tex
added couple of keywords, and some changes

\begin{enumerate}
\item We have added pseudo-code for the `Find Best Marginal Rule' subroutine of the BRS algorithm.
\item We have added methods for setting good values of our tunable parameters $W$, $k$, and $m_w$ in Section~\ref{sec:setting-paramters}.
\item Section~\ref{sec:sampling} has been significantly expanded, with details on how to utilize samples stored in memory and when to form new samples. We have also added a more detailed description and proof for our approximate dynamic-programming based algorithm for determining the best samples to form.
\item We have added an alternative convex-optimization based solution for determining the best samples.
\item Additionally, Section~\ref{sec:sampling} contains additional optimizations such as pre-fetching, and guidelines for setting the sampling parameter $minSS$. 
\item Section~\ref{sec:extensions} contains two simple extensions, namely dealing with numerical attributes, and using aggregates other than Count. 
\end{enumerate}

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
ADD-OTHER-IEEE-KEYWORDS
\end{IEEEkeywords}
}

@@

\stitle{Additional optimizations:}
There are some additional minor optimizations we can make to reduce the memory cost per sample, allowing us to store more and bigger samples. 
Suppose we have a sample $s$, and say its filter rule $f_s$ has value $v$ in column $c$. Then we know that each tuple $t$ in $T_s$ must also have value $v$ in column $c$, since it is covered by $f_s$. So we do not need to explicitly store the column $c$ value of any tuple in $T_s$. We only need to store the tuple values of columns that have a $\star$ value in $f_s$.
In addition, we may have a tuple occur in multiple samples. Instead of storing the entire tuple repeatedly, we could create a dictionary of common tuples, and only store a pointer to the tuple's dictionary entry in $T_s$.

>>>>

\begin{enumerate}
\item We have added pseudo-code for the `Find Best Marginal Rule' subroutine of the BRS algorithm.
\item The new Section~\ref{sec:setting-paramters} contains methods for setting good values of our tunable parameters $W$, $k$, and $m_w$ .
\item Section~\ref{sec:sampling} has been significantly expanded, with details on how to utilize samples stored in memory and when to form new samples. We have also added a more detailed description and proof for our approximate dynamic-programming based algorithm for determining the best samples to form.
\item We have added an alternative convex-optimization based solution for determining the best samples in Section~\ref{sec:sampling}.
\item Additionally, Section~\ref{sec:sampling} contains additional optimizations such as pre-fetching, and guidelines for setting the sampling parameter $minSS$. 
\item We added Section~\ref{sec:extensions}, which contains two simple extensions, namely dealing with numerical attributes, and using aggregates other than Count. 
\end{enumerate}

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Data Exploration, Data Summarization
\end{IEEEkeywords}
}

@@

\begin{comment}
\stitle{Additional optimizations:}
There are some additional minor optimizations we can make to reduce the memory cost per sample, allowing us to store more and bigger samples. 
Suppose we have a sample $s$, and say its filter rule $f_s$ has value $v$ in column $c$. Then we know that each tuple $t$ in $T_s$ must also have value $v$ in column $c$, since it is covered by $f_s$. So we do not need to explicitly store the column $c$ value of any tuple in $T_s$. We only need to store the tuple values of columns that have a $\star$ value in $f_s$.
In addition, we may have a tuple occur in multiple samples. Instead of storing the entire tuple repeatedly, we could create a dictionary of common tuples, and only store a pointer to the tuple's dictionary entry in $T_s$. 
\end{comment}
